%% Modified documentstyle to documentclass -- compatibility with LaTex2e
%% N. Mancell (98/03/01).

%%  ucalgthes_root.tex        (NM 98/03/01)
%   Modified   92-09-18      Add references to dissertation        D. Teale
%                            Add approval page to toc
%                            Add ref to Title Degree on approval page
%   Modified  2006-09-12     Added geometry package to set up UofC thesis margins
%                            Removed includeprompt option N. Mancell               
%
\documentclass{ucalgthes1}   
\usepackage[letterpaper,top=1in, bottom=1.22in, left=1.40in, right=0.850in]{geometry}
\usepackage{fancyhdr}
\fancyhead{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[RO,LE]{\thepage}  
%Define other usepackages here
\usepackage[plainpages=false]{hyperref}
\title{Auto-tagging Emails and Instant Messages with User Stories to Build a Knowledge Base\\ 
\bigskip for Distributed Agile Projects}
%
%            Insert the correct information between the {}
%
\author{S. M. Sohan}
\thesisyear{2010}
\thesis{thesis}    % the word dissertation can be inserted between {}
\newcommand{\thesistitle}{Auto-tagging Emails and Instant Messages with User Stories to Build a Knowledge Base for Distributed Agile Projects}
\monthname{December}
\dept{COMPUTER SCIENCE}
\degree{MASTER OF SCIENCE}
%
%                    End of supplied information
%
\begin{document}
\makethesistitle
\pagenumbering{roman}     % resets page counter to one
\setcounter{page}{1}
\chapter*{UNIVERSITY OF CALGARY \\ FACULTY OF GRADUATE STUDIES}
\thispagestyle{empty}
The undersigned certify that they have read, and recommend
to the Faculty of Graduate Studies for acceptance, a \Thesis\ entitled
``\thesistitle'' submitted by \Author\
in partial fulfillment of the requirements for the degree of
\Degree.\\

%
%                 Substitute  List of Examiners
%
\begin{signing}{Department of Academic Computing}
\signline
Supervisor, Dr. Frank Oliver Maurer \\
Department of Computer Science \\

\signline
Chairman, Dr.~John D.~Doe \\
Department of Academic Computing \\
Services  \\
\signline
Chairman, Dr.~John D.~Doe \\
Department of Academic Computing \\
Services  \\
\signline
Chairman, Dr.~John D.~Doe \\
Department of Academic Computing \\
Services  \\
\end{signing}
%
\newpage
\phantomsection
\altchapter{Abstract} 
Paragraph 1

Paragraph 2

Paragragh 3
\newpage
\phantomsection
\altchapter{Acknowledgements}
I have been blessed with the trust and support of a number of people and organizations while working on this research. In this regard, I would like to thank -

Dr. Frank Maurer and Dr. Michael Richter for your help with formulating and advancing this research. You have provided me with useful guidelines and suggestions at various steps and kept trust in me all the way.

Syed Rayhan and the Code71 team for providing me with an excellent environment for learning and innovative thinking. Working with you have been a memorable experience and helped me coming up with this research idea.

University of Calgary for your financial support without which I couldn't carry out this research.

My loving wife, Shahana, for giving me a happy family life. You have come all the way from Dhaka to Calgary to accompany me and that proved to be a lot for my well being.

My parents, S. M. Afaz Uddin and Mrs. Kh. Shirin, for inspiring me all through my life. Your continuous inspiration has given me the enthusiasm and courage at all walks of the life and this graduate research is one example of that.

Bangladesh, my country, for your promise to educate and raise me. You have given me the strong foundation to face the world.

\begin{singlespace}
\newpage
\phantomsection
\tableofcontents
\pagestyle{plain}
\newpage
\phantomsection
\listoftables
\pagestyle{plain}
\newpage
\phantomsection
\listoffigures
\pagestyle{plain}
\clearpage
\end{singlespace}
\clearpage          % otherwise tables will be numbered wrong

\pagenumbering{arabic}
\include{introduction}
\include{literature_review}
\include{taggy}
\include{empirical_evaluation}
\include{qualitative_evaluation}
\include{discussion}
\include{conclusion}
% \include{appendix1}
\end{document}
